\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-09 implementation.tex
.

@@

However, we need to explore more benchmarks to be conclusive on the
tool's performance on real world examples. Although, PWA-Rel does not
need to refine like S3CAM, and should be more scalable, it is still
constrained by the accuracy of the pwa models. Its performance can be
explained by the difficulty in finding an abstraction
($\quant_\epsilon$), which is fine enough, to result in accurate
prediction models but coarse enough to be manageable by the current
bmc tools.  To obtain a reproducible counter-example from the model
checker (and avoid false positives), the transition system should be
created from models with high accuracy, for which a finer abstraction
is required.  However, the exploration of a finer abstraction is
exponentially more complex and results in a much bigger transition
system, which the current state of the art bounded model checkers
(which use generic SMT solvers) can not handle under reasonable
resources.

>>>>

    insulin-st-1             &$Safe$ & $Safe$  & $0.0$\\
    insulin-st-2             &$Safe$ & $Safe$  & $0.0$\\
    lane change              &$Safe$ & $Safe$  & $0.0$\\
    HVAC                     &$Safe$ & $Safe$  & $0.0$\\

@@

However, we need to explore more benchmarks to be conclusive on the
tool's performance on real world examples. Although, PWA-Rel does not
need to refine like S3CAM, and should be more scalable, it is still
constrained by the accuracy of the PWA models. Its performance can be
explained by the difficulty in finding an abstraction
($\quant_\epsilon$), which is fine enough, to result in accurate
prediction models but coarse enough to be manageable by the current
bmc tools.  To obtain a reproducible counter-example from the model
checker (and avoid false positives), the transition system should be
created from models with high accuracy, for which a finer abstraction
is required.  However, the exploration of a finer abstraction is
exponentially more complex and results in a much bigger transition
system, which the current state of the art bounded model checkers
(which use generic SMT solvers) can not handle under reasonable
resources.
